Visualizations for the manuscript

### 2022-03-23 metanalysis_visualization/manuscript_Figures.Rmd
fixing meta analysis by country

```{r}
## Estimate sampling variances
```

@@

```{r}
# Random effect effects
model_meta_siteid <- metafor::rma(yi = observed, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid) 
metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```

```{r}
trends_country <- df_coefficients_boot %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
         var_boot = var(`periodduring_pandemic:time`), 
         z = mean_boot / sqrt(var_boot), 
         pvalue = pnorm(z, lower.tail = FALSE)*2 )

model_meta_country <- metafor::rma(yi = mean_boot, 
             vi = var_boot,
             measure = "MN",
             method = "FE",
  data = trends_country) 
metafor::forest(model_meta_country,
                slab = trends_country$country,
                header="Sites",
                mlab="Overall temporal trend")
```

>>>>

@@

```{r}
# Random effect effects
model_meta_siteid <- metafor::rma(yi = observed, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid)

metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                header="Sites",
                mlab="Overall periods' slope differences")
```

```{r}
trends_country <- trends_siteid %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

model_meta_country <- rma(data = trends_country, 
                          yi = pred, 
                          vi = se**2, 
                          measure = "MN", 
                          method = "DL")

forest(model_meta_country, 
       slab = trends_country$country,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```
